MLH1 Data Report

### 2018-05-29 Main_Report.rmd
removed duplicate data, added stiching to makefile

---
title: 'MLH1 Data Report'
author: "April Peterson"
date: "some date"
output: rmarkdown::github_document
---

```{r setup, echo=FALSE, include = FALSE}
#
library(knitr)
library(ggplot2)
#library(pwr)
library(plyr)
library(lattice)
library(dplyr)
setwd("C:/Users/alpeterson7/Documents/MLH1repo")
#setwd("C:/Users/April/Desktop/MLH1repo")
load(file="MLH1_data_setup.RData")
```

@@

latice plot of scatter plots for jitter plots of cell oberservations by quality. The category mean is in black and the mouse specific mean is in red.
```{r, echo=FALSE, message=FALSE,results='hide', warning=FALSE}
#what is the purpose of this block
df_list <- split(MLH1_data, (MLH1_data$category))
#remove sections which are in category but have no data
df_list <- df_list[ -c(7,14,16,22) ]
#7: PERC male, 12: KAZ female! (14:CAST female, fake data) 16:HMI female

@@

#make a new empty df. create a ddply thing with mean calculations (this is like a list for matching up later)
for(i in 1:(length(df_list))){
 # only include data with quality values, then create a ddply for specific sub-df that calqs mean by each mouse
  df_list[[i]] <- df_list[[i]][!(is.na(df_list[[i]]$quality) | df_list[[i]]$quality==""), ]
  sub_mouse_means <- ddply(df_list[[i]], .(mouse), summarise,
                       mouse_nMLH1 = mean(adj_nMLH1.foci)
  )
# this loop is going though each row of dataframes within the df.list and assining the mouse mean
  for(o in 1:length(df_list[[i]]$Original.Name)){
    df_list[[i]]$mouse_mean_MLH1[o] <- sub_mouse_means$mouse_nMLH1[ (df_list[[i]]$mouse[o] == sub_mouse_means$mouse) ]
        }
}

plot_list = list()
for (h in 1:length(df_list)) {
  pf <- ggplot(df_list[[h]],(aes(y= adj_nMLH1.foci, x= quality)))
  pf <- pf + geom_jitter(width = 0.25, aes(colour = factor(Batch)) )
  pf <- pf + geom_hline(yintercept = c( mean(df_list[[h]]$adj_nMLH1.foci) ), color="black" )
  pf <- pf + facet_wrap(~ mouse) + geom_hline(aes(yintercept = mouse_mean_MLH1), color="red")
  plot_list[[h]] =   pf
}

@@

```{r, fig.height=2, fig.width=4, echo=FALSE}
#this table is saved in the .RData file
#use kable to make tables. warning this might not work for github Rmd.
n <- kable(AP_mouse_table)
n
```

>>>>

---
title: 'MLH1 Data Report'
author: "April Peterson"
date: "29 may 2018"
output: rmarkdown::github_document
---

```{r setup, echo=FALSE, include = FALSE}
library(knitr)
library(ggplot2)
#library(pwr)
library(plyr)
library(lattice)
library(dplyr)
setwd("C:/Users/alpeterson7/Documents/MLH1repo")
#setwd("C:/Users/April/Desktop/MLH1repo")
load(file="MLH1_data_setup.RData")
```

@@

latice plot of scatter plots for jitter plots of cell oberservations by quality. The category mean is in black and the mouse specific mean is in red.
```{r, echo=FALSE, message=FALSE,results='hide', warning=FALSE}
### to integrate 'pass'/fail
### this should be in setup data

#what is the purpose of this block
df_list <- split(MLH1_data, (MLH1_data$category))
#remove sections which are in category but have no data
df_list <- df_list[ -c(7,14,16,22) ]
#7: PERC male, 12: KAZ female! (14:CAST female, fake data) 16:HMI female

@@

#make a new empty df. create a ddply thing with mean calculations (this is like a list for matching up later)
for(i in 1:(length(df_list))){
 # only include data with quality values, then create a ddply for specific sub-df that calqs mean by each mouse
  df_list[[i]] <- df_list[[i]][!(is.na(df_list[[i]]$quality) | df_list[[i]]$quality==""), ]
  sub_mouse_means <- ddply(df_list[[i]], .(mouse), summarise,
                       mouse_nMLH1 = mean(adj_nMLH1.foci)
  )
# this loop is going though each row of dataframes within the df.list and assigning the mouse mean
  for(o in 1:length(df_list[[i]]$Original.Name)){
    df_list[[i]]$mouse_mean_MLH1[o] <- sub_mouse_means$mouse_nMLH1[ (df_list[[i]]$mouse[o] == sub_mouse_means$mouse) ]
        }
}

plot_list = list()
for (h in 1:length(df_list)) {
  pf <- ggplot(df_list[[h]],(aes(y= adj_nMLH1.foci, x= quality)))
  pf <- pf + geom_jitter(width = 0.25, aes(colour = factor(Batch)) )
  pf <- pf + geom_hline(yintercept = c( mean(df_list[[h]]$adj_nMLH1.foci) ), color="black" )
  pf <- pf + facet_wrap(~ mouse) + geom_hline(aes(yintercept = mouse_mean_MLH1), color="red") 
  #theme for indiviual mice, 
  #+ theme(plot.background = element_rect(fill = "green"))
  plot_list[[h]] =   pf
}

@@

```{r, fig.height=2, fig.width=4, echo=FALSE}
#this table is 
#this table is saved in the .RData file
#use kable to make tables. warning this might not work for github Rmd.
n <- kable(AP_mouse_table)
n
```
